\chapter*{Acknowledgments}
\setheader{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

Writing a master's thesis is a difficult job and I could not have done it without the help, support and encouragement of my friends, family and peers. First and foremost, I want to thank my thesis supervisors, Daniel Scheeres and Ron Noomen, who have played pivotal roles in making this thesis possible. Thank you Daniel, for giving me the opportunity to work at your lab. I have learned a lot from you and I hope to get a chance to be your student again in future. Thank you Ron for your support while I was away in Boulder and for accommodating weekly skype meetings in your agenda. I am grateful for your patience and for never giving up on me. I want to thank Kartik Kumar, my friend and mentor, who always offered his help whenever I asked for it.
\newline\newline
It was not easy to move to Boulder, and to start a new segment of my life there. Thank you Kathleen and Antonio, for accommodating me in your home and making sure I don't have to worry about anything but my studies. I want to thank Connor and Stijn for always helping me out with any doubt I had regarding my work; and Alex for the free lessons on bouldering. Thank you Merel, Tom and Erin, for the many evenings spent together bar-hopping on the Pearl street after an intense week of work.
\newline\newline
I want to thank Gourav, for being a great friend and for traveling across towns to submit my thesis report. I am also grateful to the new friends I made after coming back to Delft, who were there to walk with me during the remainder of my thesis. Thank you Surbhi, Deepanshu, Vanshika and Sanaj for all the wonderful time spent together and treating me like family. Thank you Nilofer, for standing beside me through thick and thin.
\newline\newline
And finally, I want to thank my family for always believing in me, for letting me pursue my passion, for supporting my studies, and for always keeping my wishes above theirs. I would not have been here if it weren't for them. Thank you for everything.

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Delft, 2018
\makeatother}
\end{flushright}
